\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-10 manuscript.Rmd
Dependency fix attempt 1

```{r dependencymanager, include = FALSE}
library(packrat)
packrat::init()
```

@@

export_svg(Flowchart1) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("mFlowchart1.png")

>>>>

```{r dependencymanager, include = FALSE}
library(packrat)
packrat::init()
packrat::snapshot()
```

@@

export_svg(Flowchart1) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Manuscript.figures/Flowchart1.png")
